The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-24 paper/ms.tex
open science

We believe in open science, and have therefore made all substantive products of this research available to the interested reader. All code used to produce smear light curves is available under a GPL~v3 license at \url{https://github.com/benjaminpope/keplersmear}. All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and other stars as discussed in Section~\ref{other}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product. TRES spectra are available from \textcolor{red}{somewhere}, and all asteroseismic parameters and derived stellar parameters for the red giants in Section~\ref{rgs} are provided in an online-only table as Supplementary Material to this paper.

@@

BP acknowledges being on the traditional territory of the Lenape Nations and, today, we recognize that Manhattan continues to be the home to many Algonkian peoples. We thank the Lenape peoples for allowing us to carry out this work on the Lenape original homelands at New York University. BP and TW would like to acknowledge the Gadigal people of the Eora Nation and the Norongerragal and Gweagal peoples of the Tharawal Nation as the traditional owners of the land at the University of Sydney and the Sutherland Shire on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.

>>>>

We believe in open science, and have therefore made all substantive products of this research available to the interested reader. All code used to produce smear light curves is available under a GPL~v3 license at \url{github.com/benjaminpope/keplersmear}. All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and other stars as discussed in Section~\ref{other}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product. TRES spectra are available from \textcolor{red}{somewhere}, and all asteroseismic parameters and derived stellar parameters for the red giants in Section~\ref{rgs} are provided in an online-only table as Supplementary Material to this paper.

All smear light curves in this paper, as well as the \LaTeX{} source code used to produce this document, can be found
at \url{github.com/benjaminpope/smearcampaign}.

@@

BP acknowledges being on the traditional territory of the Lenape Nations and, today, we grecognize that Manhattan continues to be the home to many Algonkian peoples. We thank the Lenape peoples for allowing us to carry out this work on the Lenape original homelands at New York University. BP and TW would like to acknowledge the Gadigal people of the Eora Nation and the Norongerragal and Gweagal peoples of the Tharawal Nation as the traditional owners of the land at the University of Sydney and the Sutherland Shire on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.
